Apparent preferences for cognitive effort fade when multiple forms of effort

### 2021-05-19 Manuscript.Rmd
added the option to draft latex eqs automatically for mixed effects models

```{r Setups, include = FALSE, warning = FALSE}
## libraries
library(tidyverse)
library(ggfortify)
library(knitr)
library(pander) 
library(nloptr)
library(pwr)
library(lme4)
#library(lmerTest)
library(gridExtra)
library(reshape2)
library(corrplot)
library(survival)
library(patchwork)
library(data.table)

>>>>

```{r Setups, include = FALSE, warning = FALSE}
## libraries
library(tidyverse)
library(ggfortify)
library(knitr)
library(pander) 
library(nloptr)
library(pwr)
library(lme4)
#library(lmerTest)
library(gridExtra)
library(reshape2)
library(corrplot)
library(survival)
library(patchwork)
library(data.table)
# library(equatiomatic) # with the dev version, you can extract latex equations for the mixed-effects models using e.g. extract_eq(mixLogis_main_btw$Wait)
